Forklift: An Implementation of Nested Sampling for Two Objective Functions

### 2021-05-19 paper/ms.tex
Use historical example
Do Atoms and Potts

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\newcommand{\xx}{\boldsymbol{\theta}}
\newcommand{\dx}{d\boldsymbol{\theta}}
\newcommand{\data}{D}
\newcommand{\II}{I}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\todo}{\color{blue}{\bf TODO}:~}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{I introduce {\em Forklift}, an implementation of Nested Sampling (NS)
that broadens its applicability to problems with two objective functions.
I demonstrate the algorithm on three example problems:
(i) a toy problem whose partition function $Z(\beta_1, \beta_2)$ (of two
temperatures) is known, so we can compute the actual error in the reconstructed
function $Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
that is intermediate between a Lennard-Jones form and a `polymer' form; and
(iii) {\todo decide between a few options: image reconstruction with an
intractable normalizing constant in the prior, or perhaps the `Potts' example
which is a compromize between a 2D potts model and a product of many 1D
Potts models}.
A free software implementation in modern C++ is available at
\url{https://github.com/eggplantbren/Forklift}.}

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{algorithm2e}
\newcommand{\xx}{\boldsymbol{\theta}}
\newcommand{\dx}{d\boldsymbol{\theta}}
\newcommand{\data}{D}
\newcommand{\II}{I}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\todo}{\color{blue}{\bf TODO}:~}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{I introduce {\em Forklift}, an implementation of Nested Sampling (NS)
that broadens its applicability to problems with two objective functions.
I demonstrate the algorithm on three example problems:
(i) a toy problem whose partition function $Z(\beta_1, \beta_2)$ (of two
temperatures) is known, so we can compute the actual error in the reconstructed
function $Z(\beta_1, \beta_2)$; (ii) Lennard-Jones atoms in an external field;
and
(iii) a `Potts' example
which is a compromize between a 2D potts model and a product of many 1D
Potts models.
A free software implementation in modern C++ is available at
\url{https://github.com/eggplantbren/Forklift}.}
